### 2021-01-20 README.Rmd
bug fixes + R CMD check
Fix and rebuild README

# Get predicted dbh values values
predictions <- focal_vs_comp_ex %>%
  predict(posterior_param = posterior_param_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

@@

# Plot posteriors
plot_ex <- posterior_param_ex %>%
  plot_bayesian_model_parameters()
plot_ex[["lambda"]]
```

>>>>

# Get predicted dbh values values
predictions <- posterior_param_ex %>%
  predict(focal_vs_comp = focal_vs_comp_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

@@

# Plot posteriors
posterior_param_ex %>%
  autoplot(type = "intercepts")
posterior_param_ex %>%
  autoplot(type = "dbh_slopes")
posterior_param_ex %>%
  autoplot(type = "competition")
```
